Waking Up a Sleeping Rabbit:\\ On Natural-Language Sentence Generation with FF

### 2010-03-01 trunk/Papers/crisp-ff-10/abstract.tex
new abstract, copyright notice, formatting back into 4 pages

\begin{abstract}
We present a planning domain that encodes the problem of generating
natural language sentences. This domain has a number of features that
provoke fairly unusual behavior in existing planners. In particular,
we show how several techniques used in the FF planner, which has been
highly successful on IPC problems, are led astray. We discuss possible
fixes to FF's shortcomings, some of which we have already implemented,
but some of which pose interesting challenges to the AI Planning
community. The performance of our modified FF is up to several orders
of magnitude better than that of the original FF. While this makes FF
much more practical for this application, we show that it is still
quite limited with respect to the complexity of the underlying
grammar.
%We outline how other planning domains might share the
%features that make the generation domain difficult. {\bf do we? how?}
\end{abstract}

>>>>

\begin{abstract}
We present a planning domain that encodes the problem of generating
natural language sentences. This domain has a number of features that
provoke fairly unusual behavior in planners. In particular, hitherto
no existing automated planner was sufficiently effective to be of
practical value in this application. We analyze in detail the reasons
for ineffectiveness in FF, resulting in a few minor implementation
fixes in FF's preprocessor, and in a basic reconfiguration of its
search options. The performance of the modified FF is up to several
orders of magnitude better than that of the original FF, and for the
first time makes automated planners a practical possibility for this
application. Beside thus highlighting the importance of preprocessing
and automated configuration techniques, we show that the domain still
poses several interesting challenges to the development of search
heuristics.
%In particular, we show how several techniques used in the FF planner,
%which has been highly successful on IPC problems, are led astray. We
%discuss possible fixes to FF's shortcomings, some of which we have
%already implemented, but some of which pose interesting challenges to
%the AI Planning community. The performance of our modified FF is up to
%several orders of magnitude better than that of the original FF, and
%for the first time makes automated planners a pratical possibility for
%this application.
%
%. While this makes FF
%much more practical for this application, we show that it is still
%quite limited with respect to the complexity of the underlying
%grammar.
%We outline how other planning domains might share the
%features that make the generation domain difficult. {\bf do we? how?}
\end{abstract}

### 2010-03-01 trunk/Papers/crisp-ff-10/experiments.tex
new abstract, copyright notice, formatting back into 4 pages

Consider first the results for $d=0$, shown in Fig.~\ref{fig:runtimes}
(a); the lines end where the planner exceeded its five-minute
timeout. Notice that the vertical axis is logarithmic. Clearly, ``Old
FF'' (the original FF) is much too slow for practical use. The same is
true -- although to a less dramatic extent -- for LAMA, which already
takes three seconds to generate the relatively short sentence at $n=3$
and times out for larger instances. ``New preprocessor'' is FF with
only our fixes to FF's preprocess, ``New FF'' applies all fixes.
% The other two lines represent FF with the improved preprocessor,
%using the standard enforced hillclimbing strategy and the best-first
%search with helpful actions (``New FF'') respectively.  
Even the preprocessor fixes alone lead to a speed-up of at least $3$
orders of magnitude, leading to practically useful runtime -- for
instance, the 24-word sentence at $n=4$ is generated in under two
seconds. Note that, by contrast, the search configuration does not
make much of a difference here. This changes in our next experiment.

>>>>

Consider first the results for $d=0$, shown in Fig.~\ref{fig:runtimes}
(a); the lines end where the planner exceeded its five-minute
timeout. Note that the vertical axis is logarithmic. Clearly, ``Old
FF'' (the original FF) is much too slow for practical use. The same is
true -- although to a less dramatic extent -- for LAMA, which already
takes $3$ seconds to generate the relatively short sentence at $n=3$ and
times out for larger instances. ``New preprocessor'' is FF with only
our fixes to FF's preprocess, ``New FF'' applies all fixes.
% The other two lines represent FF with the improved preprocessor,
%using the standard enforced hillclimbing strategy and the best-first
%search with helpful actions (``New FF'') respectively.  
The preprocessor fixes alone lead to a speed-up of at least $3$ orders
of magnitude, leading to practically useful runtime -- e.g., the
24-word sentence at $n=4$ is generated in under two seconds. By
contrast, the search configuration does not make much of a
difference. This changes in our next experiment.
